---
title: "DANL 200: Introduction to Data Analytics<br>Project"
subtitle: "Olympics Project<br><br>" 
author: 
  - name: Lucas Rosa
    affiliations:
      - name: SUNY Geneseo
 
  - <br>
date: "`r Sys.Date()`"

format: 
  html:
    toc: true
    number-sections: true
    code-fold: false       # https://quarto.org/docs/output-formats/html-code.html
    code-summary: "Show the code"
    code-tools: true
    highlight-style: espresso # atom-one tango espresso

execute: 
  echo: true
  eval: true
  warning: false
  message: false
  fig-width: 9
---

```{r setup, include = FALSE}
library(tidyverse)
library(hrbrthemes)
library(skimr)

```

```{r}
olympic <- read_csv('/Users/lucasrosa/Downloads/olympic_games.csv')
nvars <- format(round(ncol(olympic), 0), 
                nsmall=0, 
                big.mark=",") 
nobs <- format(round(nrow(olympic), 0), 
                nsmall=0, 
                big.mark=",")
```

-   Here is the paged table using `rmarkdown::paged_table()` with the `results = 'asis'` chunk option.

```{r}
#| results: asis
#| echo: false
rmarkdown::paged_table(olympic) 
```

<br>

The number of variables is `r nvars`; the number of observations is `r nobs`.

<br>


# Introduction

My project is important because if we can find countries that have multiple years where they win the most amount of gold metals we can predict that this outcome is more likely to happen again for that country than a country its never happened for. Overall the goal of my project is to find out which country has the most likely chance of winning the most amount of gold metals in a specific year so that I can predict which country is most likely to accomplish this feat again in the future.


# Variable Description
1.Year: Year that olympics were hosted

2.game_type: Defines whether olympics were hosted in winder or summer

3.host_country: Country the olympics were hosted in 

4.host_city: City the olypics were hosted in

5.track_name: name of the track

6.athletes: The ammount of athletes in the olypics

7.teams: The number of teams in the olympics

8.competitions: The number of competitions held at the olymics

9.country: The countries that participated in olympics

10.gold: The amount of gold metals a country won

11.silver: The amount of silver metals acountry won

12.bronze: The amount of broze metals a country won
## Data Summary
```{r}
skimr::skim(olympic)
```
## Data Visualization

```{r}

top10 <- olympic %>% 
  arrange(desc(gold)) %>%
  head(10)

print(top10)

          

```



## Analysis
From my data we can see that the USSR has won the most amount of metals out of the top 10 countries that won the largest number of gold metals over 10 separate years. From this I can conclude that the USSR is most likely to win the most gold metals in future years.
## Quotes



> "Gold medal always feels great. In fact, any appreciation or acknowledgement is a great morale booster"
>
> Dutee Chand

## Inserting Figures



```{r}
ggplot(top10, aes(x = reorder(country, gold), y = gold)) +
  geom_bar(stat = "identity", fill = "gold") +
  labs(title = "Countries with the Most Gold Medals in Olympics",
       x = "Country",
       y = "Total Gold Medals") +
  theme_minimal() +
  theme(axis.text.x = element_text(angle = 45, hjust = 1))


```

## Inserting a HTML page

```{=html}
<style>iframe{height: 800px; width: 700px}</style>
<iframe height="100%" width="100%" frameborder="no"
src="https://bcdanl.shinyapps.io/01_old_faithful/">
</iframe>
```
<br><br><br><br>

# References

-   <https://www.brainyquote.com/topics/gold-medal-quotes>

-   <https://quarto.org/docs/websites/>

-   [R for Data Science](http://r4ds.hadley.nz) by [Hadley Wickham](https://hadley.nz)